---
title: "Time Varying"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Time Varying}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Another example of how to use time-varying. Let's say we want to break every 6 hours. Just add that as a feature. Here we give it a count with infinite lookback, to count the 6-hour period we're in. We also want to include the endpoint, which we encode with aggregation "event".
Finally, if there are multiple encounters per person, you can just add another row to the exposure, and tag it with another id which
gets carried forward by `time_varying()`.

```{r}
library(tv)
library(tibble)
library(dplyr)
library(lubridate)
data <- tribble(
  ~ pat_id, ~ feature, ~ datetime, ~ value,
  1, "lactate", "2021-12-31 23:00:00", 9,
  1, "lactate", "2022-01-01 03:41:00", 10,
  1, "lactate", "2022-01-01 07:00:00", 11,
  1, "blood pressure", "2022-01-01 02:00:00", 120,
  1, "blood pressure", "2022-01-01 04:00:00", 115,
  1, "blood pressure", "2022-01-01 06:00:00", 118,
  1, "6-hour", "2022-01-01 00:00:00", NA_real_,
  1, "6-hour", "2022-01-01 06:00:00", NA_real_,
  1, "6-hour", "2022-01-01 12:00:00", NA_real_,
  1, "6-hour", "2022-01-01 18:00:00", NA_real_,
  1, "event", "2022-01-01 08:00:00", NA_real_,
  1, "event", "2022-01-01 13:00:00", NA_real_
) %>%
  mutate(datetime = as_datetime(datetime))

specs <- tribble(
  ~ feature, ~ use_for_grid, ~ lookback_start, ~ lookback_end, ~ aggregation,
  "lactate", TRUE, 0, Inf, "ts",
  "lactate", TRUE, 0, Inf, "lvcf",
  "blood pressure", FALSE, 0, 7200, "ts", # two hours
  "blood pressure", FALSE, 0, 7200, "lvcf", # two hours
  "6-hour", TRUE, 0, Inf, "n",
  "event", TRUE, 0, 0, "event"
)

exposure <- tibble(
  pat_id = 1,
  encounter = 1:2, # optional id
  exposure_start = as_datetime(c("2022-01-01 00:00:00", "2022-01-01 08:00:00")),
  exposure_stop = as_datetime(c("2022-01-01 08:00:00", "2022-01-01 13:00:00")),
)

time_varying(data, specs, exposure = exposure, time_units = "seconds", n_cores = 1) %>%
  arrange(pat_id, row_start)

```

Note that the lactate lab from 2021 does not contribute to a new row because it is not inside the exposure window.
Note also that the lookback is ignored for aggregation of type "event".




